Appendix S2: Data Exploration

### 2022-04-28 ms/data_exploration.Rmd
Update data exploration

```{r plot-raw-data, fig.height = 8}
ggplot(biodiv_ferns_cent_no_outliers, aes(x = .panel_x, y = .panel_y)) + 
  geom_point(alpha = 0.5, shape = 16, size = 0.5) + 
  geom_smooth() +
  facet_matrix(
    cols = vars(temp, precip, precip_season, percent_apo),
    rows = vars(richness, pd_obs_z, fd_obs_z, rpd_obs_z, rfd_obs_z))
```

>>>>

```{r plot-raw-data, fig.height = 8}
biodiv_ferns_cent_no_outliers %>%
  # Convert precipitation to meters so 
  # the numbers don't overlap on the x-axis
  mutate(precip = precip/1000) %>%
  ggplot(aes(x = .panel_x, y = .panel_y)) + 
  geom_point(alpha = 0.5, shape = 16, size = 0.5) + 
  geom_smooth() +
  facet_matrix(
    cols = vars(temp, precip, precip_season, percent_apo),
    rows = vars(richness, pd_obs_z, fd_obs_z, rpd_obs_z, rfd_obs_z))
```
